Examining background gene lists using simulation - comparison of different enrichment techniques

### 2024-09-12 analysis/sim/run_simpw.Rmd
more sims
sims
savedata at end
fig3 boxplot with mean

SIMS=32
#run 1000 sims
FRAC_DE=0.05
FC=0.5
N_REPS=3
DGE_FUNC="deseq2"
SUM_COUNT=2e7
VARIANCE=c(0,0.1,0.2,0.3,0.4,0.5,0.6)

@@

par(mfrow=c(1,3))
par(mar=c(c(9.1, 3.5, 2.1, 1.1) ))
boxplot(prec,cex=0,main="precision",ylab="",col="white",las=2)
beeswarm(prec,add=TRUE,col="black",pch=19)
boxplot(rec,cex=0,main="recall",ylab="",col="white",las=2)
beeswarm(rec,add=TRUE,col="black",pch=19)
boxplot(f1,cex=0,main="F1 index",ylab="",col="white",las=2)
beeswarm(f1,add=TRUE,col="black",pch=19)

png("fig3_box.png", width=7,height=5,units="in",res=150,pointsize=12)
par(mar=c(c(9.1, 3.5, 2.1, 1.1) ))
par(mfrow=c(1,3))
boxplot(prec,cex=0,main="precision",ylab="",col="white",las=2)
beeswarm(prec,add=TRUE,col="black",pch=19)
boxplot(rec,cex=0,main="recall",ylab="",col="white",las=2)
beeswarm(rec,add=TRUE,col="black",pch=19)
boxplot(f1,cex=0,main="F1 index",ylab="",col="white",las=2)
beeswarm(f1,add=TRUE,col="black",pch=19)
dev.off()

pdf("fig3_box.pdf", width=7,height=5,pointsize=12)
par(mar=c(c(9.1, 3.5, 2.1, 1.1) ))
par(mfrow=c(1,3))
boxplot(prec,cex=0,main="precision",ylab="",col="white",las=2)
beeswarm(prec,add=TRUE,col="black",pch=19)
boxplot(rec,cex=0,main="recall",ylab="",col="white",las=2)
beeswarm(rec,add=TRUE,col="black",pch=19)
boxplot(f1,cex=0,main="F1 index",ylab="",col="white",las=2)
beeswarm(f1,add=TRUE,col="black",pch=19)
dev.off()

@@

>>>>

SIMS=1000
#run 1000 sims
FRAC_DE=0.05
FC=0.5
N_REPS=3
DGE_FUNC="deseq2"
SUM_COUNT=2e7
VARIANCE=c(0,0.1,0.2,0.3,0.4,0.5,0.6)

@@

par(mfrow=c(1,3))
par(mar=c(c(9.1, 3.5, 2.1, 1.1) ))
boxplot(prec,cex=0,main="precision",ylab="",col="white",las=2)
beeswarm(prec,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(prec,mean),add=TRUE,col="black",pch="x",cex=1.0)
boxplot(rec,cex=0,main="recall",ylab="",col="white",las=2)
beeswarm(rec,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(rec,mean),add=TRUE,col="black",pch="x",cex=1.0)
boxplot(f1,cex=0,main="F1 index",ylab="",col="white",las=2)
beeswarm(f1,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(f1,mean),add=TRUE,col="black",pch="x",cex=1.0)

png("fig3_box.png", width=7,height=5,units="in",res=150,pointsize=12)
par(mar=c(c(9.1, 3.5, 2.1, 1.1) ))
par(mfrow=c(1,3))
boxplot(prec,cex=0,main="precision",ylab="",col="white",las=2)
beeswarm(prec,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(prec,mean),add=TRUE,col="black",pch="x",cex=1.0)
boxplot(rec,cex=0,main="recall",ylab="",col="white",las=2)
beeswarm(rec,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(rec,mean),add=TRUE,col="black",pch="x",cex=1.0)
boxplot(f1,cex=0,main="F1 index",ylab="",col="white",las=2)
beeswarm(f1,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(f1,mean),add=TRUE,col="black",pch="x",cex=1.0)
dev.off()

pdf("fig3_box.pdf", width=7,height=5,pointsize=12)
par(mar=c(c(9.1, 3.5, 2.1, 1.1) ))
par(mfrow=c(1,3))
boxplot(prec,cex=0,main="precision",ylab="",col="white",las=2)
beeswarm(prec,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(prec,mean),add=TRUE,col="black",pch="x",cex=1.0)
boxplot(rec,cex=0,main="recall",ylab="",col="white",las=2)
beeswarm(rec,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(rec,mean),add=TRUE,col="black",pch="x",cex=1.0)
boxplot(f1,cex=0,main="F1 index",ylab="",col="white",las=2)
beeswarm(f1,add=TRUE,col="darkgray",pch=19)
beeswarm(lapply(f1,mean),add=TRUE,col="black",pch="x",cex=1.0)
dev.off()

@@

save.image("run_simpw.Rdata")
